\Title

### 2021-12-20 manuscript/manuscript.tex
Updated manuscript
Update manuscript.tex

\newcommand{\AuthorAffil}{
	{\large
		J. John Savio$^{1,2}$
		V. Yatheesh$^{1,*}$
		R. Sheldon$^{1}$
		M. Kallathian$^{1}$
		Pratima Kessarkar$^{1}$}\\
	{\large
		Kuldeep Kumar$^{1}$
		P. Mahesh$^{1}$
		Subhashree Mishra$^{1}$
		Swati Verma$^{1}$
	}
	\\[0.4cm]
	{\small $^1$ CSIR -  National Institute of Oceanography, Dona Paula, Goa -  403 004, India}
	\\
	{\small $^2$ School of Earth, Ocean and Atmospheric Sciences, Goa University, Taleigao Plateau, Goa -  403 206, India}
	\\
	{\small $^*$ Corresponding author e-mail: yatheesh@nio.org}
}
\newcommand{\DOI}{doi:\href{https://doi.org/10.xxxx/jess/xxxxxx}{10.xxxx/jess/xxxxxx}}
\newcommand*{\doi}[1]{doi:\href{http://dx.doi.org/#1}{#1}} %% To give hyperlink to DOI's

\usepackage[left=0.7in,right=0.7in,top=0.9in,bottom=0.8in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage[round]{natbib}
\hbadness=99999
%%\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
	allcolors=blue,
	pdftitle={\Title},
	pdfauthor={\Author},
}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{caption}
\fancyhf{}
\lhead{
	\fontsize{9pt}{12pt}\selectfont
	\Author{}, 2021, \DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\title{\Title}
\author{\AuthorAffil}
\date{
\normalsize
Manuscipt Received - xx June 2021; Revised - xx October 2021; Accepted - 05 November 2021
\\[0.4cm] 
\justifying{
This is a pre-copyedited, author-produced version of an article accepted for publication in \textit{\Journal{}} following peer review. The version of record "\textit{John Savio, J., Yatheesh, V., Sheldon, R., Kallathian, M., Kessarkar, P., Kumar, K., Mahesh, P., Mishra, S., \&  Verma, S., 2021. \Title{}, \Journal{},}\ " is available online at: \DOI{}
}}
\maketitle

@@

The authors are grateful to Prof. Sunil Kumar Singh, Director, CSIR-National Institute of Oceanography (CSIR-NIO), Goa, India, for providing ship time and granting permission to publish this work. This study forms a part of PhD work of JJS at Goa University. JJS thank Council of Scientific \& Industrial Research (CSIR), New Delhi, India, for the financial support under Junior Research Fellowship (Grant No. 31/026(0321)/2019-EMR-I). The cooperation and support received from the Captain and his operational team onboard \textit{RV Sindhu Sadhana} during the expedition SSD-073 are acknowledged. We thank Dr. V.J. Loveson, Head, Geological Oceanography Division for useful discussions, and Mr. S. Gautham for the help extended in processing the bathymetry data. We are grateful to an anonymous reviewer for his constructive review and valuable suggestions that improved our manuscript, and to Dr. N.V. Chalapathi Rao for editorial handling. All figures were drafted with the GMT software  \citep{Wessel2019}. This is NIO contribution xxxx.

>>>>

\newcommand{\AuthorAffil}{
	{\large
		J. John Savio$^{1,2}$,
		V. Yatheesh$^{1,*}$,
		R. Sheldon$^{1}$,
		M. Kallathian$^{1}$,
		Pratima Kessarkar$^{1}$},\\
	{\large
		Kuldeep Kumar$^{1}$,
		P. Mahesh$^{1}$,
		Subhashree Mishra$^{1}$,
		and Swati Verma$^{1}$
	}
	\\[0.4cm]
	{\small $^1$ CSIR - National Institute of Oceanography, Dona Paula, Goa -  403 004, India}
	\\
	{\small $^2$ School of Earth, Ocean and Atmospheric Sciences, Goa University, Taleigao Plateau, Goa -  403 206, India}
	\\
	{\small $^*$ Corresponding author e-mail: yatheesh@nio.org}
}
\newcommand{\DOI}{\href{https://doi.org/10.xxxx/jess/xxxxxx}{https://doi.org/xxxxxx}}
\newcommand*{\doi}[1]{doi:\href{http://dx.doi.org/#1}{#1}} %% To give hyperlink to DOI's

\usepackage[left=0.7in,right=0.7in,top=0.9in,bottom=0.8in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage[round]{natbib}
\hbadness=99999
%%\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
	allcolors=blue,
	pdftitle={\Title},
	pdfauthor={\Author},
}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{caption}
\fancyhf{}
\lhead{
	\fontsize{9pt}{12pt}\selectfont
	\Author{}, Accepeted article, \textit{\Journal{}}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\title{\Title}
\author{\AuthorAffil}
\date{
\normalsize
Manuscipt Received - 12 May 2021; Revised - October 2021; Accepted - 05 November 2021
\\[0.4cm] 
\justifying{
This is a pre-copyedited, author-produced version of an article accepted for publication in \textit{\Journal{}} following peer review. The version of record "\textit{John Savio, J., Yatheesh, V., Sheldon, R., Kallathian, M., Kessarkar, P., Kumar, K., Mahesh, P., Mishra, S., \&  Verma, S., 2022. \Title{}, \Journal{},}\ " is available online at: \DOI{}
}}
\maketitle

@@

The authors are grateful to Prof. Sunil Kumar Singh, Director, CSIR-National Institute of Oceanography (CSIR-NIO), Goa, India, for providing ship time and granting permission to publish this work. This study forms a part of PhD work of JJS at Goa University. JJS thank Council of Scientific \& Industrial Research (CSIR), New Delhi, India, for the financial support under Junior Research Fellowship (Grant No. 31/026(0321)/2019-EMR-I). The cooperation and support received from the Captain and his operational team onboard \textit{RV Sindhu Sadhana} during the expedition SSD-073 are acknowledged. We thank Dr. V.J. Loveson, Head, Geological Oceanography Division for useful discussions, and Mr. S. Gautham for the help extended in processing the bathymetry data. We are grateful to an anonymous reviewer for his constructive review and valuable suggestions that improved our manuscript, and to Dr. N.V. Chalapathi Rao for editorial handling. All figures were drafted with the GMT software  \citep{Wessel2019}. This is NIO contribution 6836.
